Extended Data

### 2021-11-15 doc/manuscript/Dow_manuscript_Nature.Rmd
Update Dow_manuscript_Nature.Rmd

Here, we evaluate how early spring temperatures affect stem growth phenology, growth rates, and annual growth of temperate deciduous trees in two forests and annual growth across forests spanning eastern North America. To test the assumption that warmer springs lead to an extension of the growing season we used measurements from 465 dendrometer bands across two deciduous mid-atlantic forests. To test whether spring temperatures were consistently positively correlated with annual ring-width Index (RWI; tree-ring width which has been standardized for age) we used `r n_chronologies` tree-ring chronologies from `r n_cores_sites` forests across eastern North America.

@@

Canopy foliage phenology data for the years 2001-2018 were extracted for SCBI and Harvard Forest from the MCD12Q2 V6 Land Cover Dynamics product (a.k.a. MODIS Global Vegetation Phenology product)[@friedl_mcd12q2_2019] via Google Earth Engine. Data were extracted for the pixel containing the NEON tower at each site. Using daily MODIS 2-band Enhanced Vegetation Index data (EVI2) at a spatial resolution of 500m, the product yields the timing of phenometrics (vegetation phenology) over each year, including timing of greenup, midgreenup, and senescence as used in this study. 
 <!--Climate -->

>>>>

Here, we evaluate how early spring temperatures affect stem growth phenology, growth rates, and annual growth of temperate deciduous trees in two forests and annual growth across forests spanning eastern North America. 
To test the assumption that warmer springs extend the period of stem growth, we used measurements from 465 dendrometer bands across two deciduous forests. 
To test whether spring temperatures were consistently positively correlated with annual ring-width Index (RWI; tree-ring width which has been standardized for age) we used `r n_chronologies` tree-ring chronologies from `r n_cores_sites` forests across eastern North America.

@@

Canopy foliage phenology data for the years 2001-2018 were extracted for SCBI and Harvard Forest from the MCD12Q2 V6 Land Cover Dynamics product (a.k.a. MODIS Global Vegetation Phenology product)[@friedl_mcd12q2_2019] via Google Earth Engine. Data were extracted for the pixel containing the NEON tower at each site. Using daily MODIS 2-band Enhanced Vegetation Index data (EVI2) at a spatial resolution of 500m, the product yields the timing of phenometrics (vegetation phenology) over each year, including timing of greenup, midgreenup, and senescence as used in this study.

 <!--Climate -->
